The Wolf in Sheep's Clothing\\ Subversive Adversarial Agent Identification

### 2016-08-04 article.tex
Let floats go where they want, we can force them into specific places once document is near final
Adds first draft of abstract

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}

@@

\begin{table}[h]
\label{table_example}
\begin{center}
\begin{tabular}{|c|c|}
\hline
State & Control\\
\hline
$x,y,\theta,v_f,v_\theta$ & $a_f,a_\theta$\\
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{Path_comp_uncomp}
\caption{The left shows the uncompromised map made up of states avoiding some area and the right shows a compromised map where the states do cross the same area. In this case the state obtained from the particle filter mean, demonstrated in blue, would likely yield a more compromised probability}
\label{fig:compmaps}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr1}
\caption{The initial communication with the central frame is made here. Each database, in its encrypted form, is created to be placed with each corresponding agent.}
\label{fig:TopicIntr1}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr2}
\caption{Topic Interaction with node- As new agents are populated, the external host lists are updated. Hence, when the topic handler retrieves the Host Lists from all the connection objects, the nodes in the current system will have an accurate overview of which topics are being published elsewhere based on the MAC of each external agent.}
\label{fig:TopicIntr2}
\end{figure}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Mobile robot security is a rapidly developing area of interest in robotics.As mobile robotic systems become more present, the need for secure and reliable state estimation systems continues to grow. The increasing coverage of wireless networks and density of network cyber-physical systems has lead to an opportunity for distributed systems coordinated between multiple agents. This paper proposes a distributed state estimation system using Kalman filters with secure ad-hoc channel communications between the agents. This system is implemented on the TurtleBot platform using the Robot Operating System, and performance is also evaluated in the Gazebo simulator.
\end{abstract}

@@

\begin{table}[]
\label{table_example}
\begin{center}
\begin{tabular}{|c|c|}
\hline
State & Control\\
\hline
$x,y,\theta,v_f,v_\theta$ & $a_f,a_\theta$\\
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[]
\centering
\includegraphics[width=0.4\textwidth]{Path_comp_uncomp}
\caption{The left shows the uncompromised map made up of states avoiding some area and the right shows a compromised map where the states do cross the same area. In this case the state obtained from the particle filter mean, demonstrated in blue, would likely yield a more compromised probability}
\label{fig:compmaps}
\end{figure}

@@

\begin{figure}[]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr1}
\caption{The initial communication with the central frame is made here. Each database, in its encrypted form, is created to be placed with each corresponding agent.}
\label{fig:TopicIntr1}
\end{figure}

@@

\begin{figure}[]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr2}
\caption{Topic Interaction with node- As new agents are populated, the external host lists are updated. Hence, when the topic handler retrieves the Host Lists from all the connection objects, the nodes in the current system will have an accurate overview of which topics are being published elsewhere based on the MAC of each external agent.}
\label{fig:TopicIntr2}
\end{figure}
